### 2012-05-09 GUIErrorDetector/paper/conclusion.tex
More future work in conclusion

>>>>

%\item
\textbf{Generalization.}
We have applied our graph reachability analysis to one specific, but
important, problem.  There is a rich history of testing and analysis
problems being cast as reachability (e.g.,~\cite{RepsHS95}).  In future
work, we plan to formulate other problems, such as detecting security
vulnerabilities, as path reachability, and to apply our scalable analysis
to them.
